
This is Hugo ChunHo Lin, a senior majoring in Atmospheric 
Science, and actively working towards a minor in 
Computer Science at National Central University. 
I am reaching out to express my keen interest in 
the \textbf{"Software Development and Test"} position at 
\company. The primary aim of this letter is to 
underscore my qualifications as a strong candidate 
for \company and convey my expectations regarding 
the company. I firmly believe that my skills and 
experiences closely align with the prerequisites 
for this role.

I have been learning programming-related skills for just two years. During these two years, I have dedicated a significant amount of my after-school time to self-study. I keep up with the latest technology articles and whenever anyone posts updates on software technology in social platforms, I dive into it. After learning new techniques, I always strive to incorporate them into my projects. I even try to apply the latest technology to my past projects. As a result, I maintain a daily commitment to learning and improving.

I am also passionate about sharing what I've learned with others, while also enjoying telling my own story. That's why I became an \textbf{AWS Cloud Ambassador}. I aim to transform my skills and experiences into inspiring stories to encourage more people on a similar path. I am well on my way in this journey.

Through my internship experience at Pegatron, I have accumulated a wealth of career experiences. I have used Scrum agile development to \textbf{organize work tasks, led internship project teams in coordinating projects, and managed meeting content}. I applied my experience on GitHub to the development process and created LLM, a project that allows direct voice control of a simulated factory arm. It earned \textbf{the second place at the project demo stage}, presented in front of the CTO and other senior engineers.

Lastly, I want to reflect the unique qualities that my internship at Pegatron and the good friends I met at AWS have noted about me. Most often, my peers would ask me, "How do you learn so quickly and acquire so much knowledge?" \textbf{I believe I am still seeking the answer to that question, constantly striving to improve myself}. However, I do know that I am doing what I love and continuing to write my own story. I would like to be a part of eCloudture's internship program and contribute to my own software journey.

As an intern, I am eager to learn from "experienced professionals, work collaboratively with team members, and contribute ideas to meaningful projects." I am a self-discipline, quick learner, detail-oriented person, and can work effectively under pressure.

Thank you for considering my application. 
I would be honored to have the opportunity to 
discuss my qualifications further and learn more a
bout the position.
