
I am Hugo ChunHo Lin, currently in my senior year at National Central University, majoring in Atmospheric Science, and actively working towards a minor in Computer Science and Information Engineering. I am reaching out to express my keen interest in the \textbf{"RD Intern - Backend"} position at your company, Tomofun. The primary aim of this letter is to underscore my qualifications as a strong candidate for Tomofun and convey my expectations regarding the company. I firmly believe that my skills and experiences closely align with the prerequisites for this role.

Currently, I am serving as a \textbf{Campus Ambassador for AWS Educate} in the role of Technical Support. My primary responsibilities include gaining a comprehensive understanding of AWS services and developing technical workshops that are accessible to beginners and those with an interest in programming. In a recent workshop, I led a session where we utilized Lex, an intelligent voice assistant, in conjunction with Lambda services to create a chatbot-driven game. This experience allowed participants to explore the benefits of voice assistants and gain a better understanding of AWS services.

Furthermore, I am in the process of planning the next workshop, where I will be integrating services such as \textbf{Lambda, S3, and API Gateway} to create a personal business card using LINE BOT. This project aims to enable effective networking and social interaction through LINE in professional settings. I believe that these experiences have prepared me to excel in a role at Tomofun. \textit{To prepare for these workshops, I have become accustomed to reading AWS official documentation and simplifying complex technical concepts for effective communication with others.} This skill has proven invaluable in various aspects of my work, from daily meetings to document writing.

In the summer of 2023, I also worked as a \textbf{Software Engineering Intern at Pegatron Corporation.} During this internship, I not only developed Machine Learning products but also gained valuable experience in Scrum agile development processes. My primary responsibility during this internship was to train an LLM model, enabling virtual robotic arms to be controlled through conversational means to complete specified tasks. I integrated software development techniques into the project, and through two months of dedicated effort, I achieved significant improvements. \textbf{By implementing Prompt Engineering, I increased support from 6 to 11 scenarios, an 83\% enhancement, and the model's accuracy improved to 80\%, now accommodating four objects, up from two.}

Additionally, the development process of this project introduced me to \textbf{Scrum}. We went through two sprints, and before the start of each sprint, I dedicated substantial time to clarify the work scope and break down tasks into units lasting from half an hour to one hour. This meticulous approach allowed me to better track workflow and make precise daily work and meeting arrangements. Having clarified the work scope before starting each sprint, I could leverage one of Scrum's most significant advantages: the ability to swiftly adjust my tasks in response to unexpected developments, ensuring the smooth progress of the sprint.

I believe that the experience I gained in Scrum development will enable me to excel in the role of Backend Intern at Tomofun and help me quickly adapt to the company's working environment.

Lastly, I'd like to share my side project experiences. I'm currently working on developing a \textbf{multi-user chatroom using the Go Language.} The project aims to implement a multi-user chatroom using socket programming. This is my first Go Language project, and I intend to gain a deeper understanding of Go's application in backend development. \textbf{I hope to leverage this project to explore Go's advantages in multithreading and delve into system-related design.}

Additionally, \textbf{my strongest programming language is Python}, and I have used \textbf{Flask and FastAPI for backend development.} Among my projects, I've developed two Line Bots. One was created with the aim of incorporating the concept of reducing food waste into a ordering system for sustainability. \textbf{In the week the bot officially launched, it successfully attracted 300 users and facilitated product listings for restaurants as well as customer purchases, contributing to sustainability efforts.} My other Line Bot combines machine learning image recognition technology to encourage recycling. \textbf{This idea earned me second place in the Weather Hackathon competition, along with a sustainability special award.}

Currently, I am working on a \textbf{learning platform, "SIMPLE AI," using FastAPI.} My goal is to make machine learning accessible to those who do not have programming experience by creating web interfaces that interact with users. Throughout these development experiences, I have frequently utilized \textbf{Git} for version control and management tools and implemented \textbf{GitHub Action for CI/CD processes}. I have also integrated \textbf{Docker for environment deployment testing.} I believe these experiences will greatly enhance my proficiency in the development process.

With the various experiences mentioned above, I am excited to apply my skills and knowledge to \textbf{World-Class projects} with brief confidence. As an intern, I am eager to learn from \textbf{\emph{experienced professionals, work collaboratively with team members, and contribute ideas to meaningful projects.}} I am a self-discipline, quick learner, detail-oriented person, and can work effectively under pressure.

Thank you for considering my application. I would be honored to have the opportunity to discuss my qualifications further and learn more about the position.