I am Hugo ChunHo Lin. I am writing to 
express my interest in the "Machine 
Learning Intern Program" at your company.
As a highly motivated and adaptable individual, 
I believe that my skills and experiences 
make me a strong fit for this role.

As a third-year student majoring in Atmospheric 
Sciences and also pursuing second major in 
Computer Science at National Central University.
With this academic career, I have gained a solid
foundation in Data Science, Computer Science, and
Programming Languages such as "Python, c/c++, Java, etc."
I have also completed the coursework in Machine Learning,
Neural Networks, Data Structure, Algotithmics, etc. 
Additionally, I have participated in two Machine 
Learning projects, the fisrt, I used Random Forest 
to analyze and predict the percentage of rainfall,
and another I used CNN to distinguish the handwriting
number.

With the extracurricular activities, I am currently 
the TAs in the course "Freshman English", which 
allows me to continually improve my English language 
skills. I have also work as "Website Administrator" to
manage the data in website, and server maintenance.
In particular, I have been the member of @NCUFresh Team, which
responsible for providing information to incoming freshmen, 
and our main objective was to develop a website to present the details.
In this progress, it's the first time I learn 
about large-scale projects management and task delegation,
which was also the period when I made the most significant 
progress in improving my Computer Science skills.

Therefore, with above of essential experiences, I am excited
to apply my skills and knowledge to World-Class projects
with brief confidence. As an intern, I am eager to learn
from experienced professionals, work collaboratively with 
team members, and contribute ideas to meaningful projects.
I am a self-discipline, quick learner, detail-oriented person, 
and can work effectively under pressure.

Thank you for considering my application. 
I would be honored to have the opportunity 
to discuss my qualifications further and 
learn more about the position.