
I am Hugo ChunHo Lin, a third-year student majoring in Atmospheric Sciences and pursuing a second major in Computer Science at National Central University. I am writing to express my interest in the \textbf{"Software Engineering Intern Program"} at your company. As a highly motivated and adaptable individual, I believe that my skills and experiences make me a strong fit for this role.

With my academic career, I have come to realize how deeply involved I am in the fields of \textbf{Computer Science and Data Science}. Through my coursework, I have gained a strong foundation in \textit{\textbf{Data Science, Computer Science, and various programming languages including Python, C/C++, Java, among others.}} Furthermore, I have completed courses in topics such as \textit{\textbf{Machine Learning, Neural Networks, Data Structures, and Algorithms, Numerical Analysis, among others.}}

I implemented several ML skills in the projects to accumulate hands-on experience. 
I utilized \textbf{random forest} to analyze and predict the percentage of rainfall, aiming to acquire a more precise rainfall prediction than the traditional methods in the meteorology(Numerical Weather Prediction). 
I possess experience in creating a \textbf{food ordering system} that incorporates LINE BOT. The aim of this project was to tackle the issue of food waste by providing a delivery service for excess food. Utilizing \textbf{Python's Flask framework}, I designed and developed the system with features such as product listings and purchase inquiries. Additionally, I developed the \textbf{API for client-side communication}. This project allowed me to gain a \textbf{more comprehensive understanding of front-end and back-end development design processes, as well as database integration}.
Plus, I created a \textbf{workout app} that allows users to track their exercise performance and schedule workouts. Throughout this process, I gained expertise in \textbf{object-oriented programming and GUI design by utilizing JavaFX framework} in the Java language.
Above all, my experiences have made me adept at applying various ML frameworks and tools, such as \textbf{Keras, Tensorflow, NUMPY, and Pandas}. Additionally, I have experience in \textbf{server configuration, app design, and system design} using languages such as Python and Java. This background has made me a strong candidate for the \textbf{Software Engineering Intern Program}. 

After sharing my academic experiences, I would like to talk about my work experiences.
I am currently serving as a \textbf{TAs} in the course "Freshman English", which provides me with the opportunity to \textbf{\textit{continuously enhance my English language skills and stay up-to-date with the latest global developments and trends}}. The most important thing is that with this new knowledge, we aim to design a lesson that will allow us to interact with students entirely in English and effectively communicate the complete information to them and facilitate in-depth discussions with them to ensure a thorough understanding of the material. 
What's more, I have also worked as a \textbf{Website Administrator}, where I was responsible for \textbf{\textit{managing website data and maintaining the server}}. While in this position, 
I also launched a project aimed at developing a system to streamline our existing workflow and facilitate the review of students' course enrollment. The goal was to improve the efficiency of the process and make it more convenient for us to manage and track student progress. 
During my time in this role, although I initiated the project, there were still many details that required discussion and delegation with my partner. Through this process, I not only gained experience in\textbf{ Linux commands, server management, and database administration}, but more importantly, I honed my \textbf{communication skills} to ensure the success of our project.

Outside of my academic and work experience, I would like to talk about my involvement in extracurricular activities. I have been the member of \textbf{@NCUFresh Team}, which is responsible for providing information to incoming freshmen, and our main objective was to develop a website to present the details. During my time there, I was in charge of the \textbf{\textit{\href{https://ncufresh22tmp.le37.tw/blog/}{NCUBlog}}} page, which was a new function added to the website. I integrated all the information into the blog format, resulting in almost every article getting \textit{\textbf{up to 1000 views}}. Throughout the project, we focused on observing user needs and figuring out how to effectively distribute our content. This experience was also suitable for Dcard to develop a product that caters to a large user base. Furthermore, it was my first time managing large-scale projects and delegating tasks, which helped me make a significant progress in improving my computer science skills. Plus, I am currently working as the member of the \textbf{@NCUApp Team} responsible for refactoring the user interface and ideating new features, such as product listings, map functionality, etc., to provide an application for use by all faculty and students at NCU. It also provides me with the opportunity to collaborate with my teammates to manage large-scale projects and improve my communication skills through continuous training.

With the various experiences mentioned above, I am excited to apply my skills and knowledge to \textbf{World-Class projects} with brief confidence. As an intern, I am eager to learn from \textbf{\emph{experienced professionals, work collaboratively with team members, and contribute ideas to meaningful projects.}} I am a self-discipline, quick learner, detail-oriented person, and can work effectively under pressure.

Thank you for considering my application. I would be honored to have the opportunity to discuss my qualifications further and learn more about the position.

