
I am Hugo ChunHo Lin. I am writing to express my interest in the \textbf{"Machine Learning Intern Program"} at your company. As a highly motivated and adaptable individual, I believe that my skills and experiences make me a strong fit for this role.

As a third-year student majoring in \textbf{\emph{Atmospheric Sciences}} and also pursuing second major in \textbf{\emph{Computer Science}} at National Central University. With this academic career, I have come to realize how deeply involved I am in the fields of Computer Science and Data Science. Through my coursework, I have gained a strong foundation in \textbf{Data Science, Computer Science, and various programming languages including Python, C/C++, Java, among others.} Furthermore, I have completed courses in topics such as \textbf{Machine Learning, Neural Networks, Data Structures, and Algorithms, among others.}
% I have realized that how much I involved in the Computer Science and Data Science, also I have gained a solid foundation in \textbf{Data Science, Computer Science, and Programming Languages such as "Python, c/c++, Java, etc."} I have also completed the coursework in \textbf{Machine Learning, Neural Networks, Data Structure, Algorithms, etc.} 
Additionally, I implemented several ML skills in two projects to accumulate hands-on experience. 
First, I utilized random forest to analyze and predict the percentage of rainfall, aiming to acquire a more precise rainfall prediction than the traditional methods in the meteorology. 
Second, I implemented CNN model with Keras to recognize 0 to 9 handwriting numbers for deeper understanding of modern ML models. These experiences help me to be adept at the application of several ML frameworks and ML-related tools such as \textbf{Keras, Tensorflow, NUMPY, Pandas}, enabling me to be eligible for the ML intern program.

% Additionally, I have participated in two Machine Learning projects, the first one, I used \textbf{\emph{Random Forest}} to analyze and predict the percentage of rainfall, and another I used \textbf{\emph{CNN}} to distinguish the handwriting number. This made me get used to the tools with Machine Learning such as \textbf{"Keras, tensorflow, Numpy, Pandas, etc."}

After sharing my academic experiences, I would like to talk about my work experiences.
I am currently serving as a \textbf{TAs} in the course "Freshman English", which provides me with the opportunity to continuously enhance my English language skills and stay up-to-date with the latest global developments and trends. The most important thing is that with this new knowledge, we aim to design a lesson that will allow us to interact with students entirely in English and effectively communicate the complete information to them.
I have also worked as \textbf{Website Administrator}, where I was responsible for managing website data and maintaining the server. While in this position, 
I also launched a project aimed at developing a system to streamline our existing workflow and facilitate the review of students' course enrollment. The goal was to improve the efficiency of the process and make it more convenient for us to manage and track student progress.

After discussing my academic and work experiences, I would like to talk about my involvement in extracurricular activities. I have been the member of \textbf{@NCUFresh Team}, which responsible for providing information to incoming freshmen, and our main objective was to develop a website to present the details. During my time there, I was in charge of the NCUBlog page, which was a new function added to the website. I integrated all the information into the blog format, resulting in almost every article getting up to 1000 views. Throughout the project, we focused on observing user needs and figuring out how to effectively distribute our content. This experience was also suitable for Dcard to develop a product that caters to a large user base. Furthermore, it was my first time managing large-scale projects and delegating tasks, which helped me make significant progress in improving my computer science skills.

% In this progress, we kept observe what is totally the user need and how to spread the content we made. And this is also the point suit for \textbf{Dcard} to develop the product satisfy the experience with a huge amount of users. Also, it's the first time I learn about large-scale projects management and tasks delegation, which was also the period when I made the most significant progress in improving my Computer Science skills. 

Therefore, with the above essential experiences, I am excited to apply my skills and knowledge to \textbf{World-Class projects} with brief confidence. As an intern, I am eager to learn from \textbf{\emph{experienced professionals, work collaboratively with team members, and contribute ideas to meaningful projects.}} I am a self-discipline, quick learner, detail-oriented person, and can work effectively under pressure.

Thank you for considering my application. I would be honored to have the opportunity to discuss my qualifications further and learn more about the position.